### 2020-02-17 Common/chapters/transfer_learning.tex
Julien and Johan: TL chapter - introduction

\chapter{Improving performance using transfer learning}
\label{ch:transfer_learning}

What we do: improve cancer detection/classification on medical imaging
How we do it: transfer learning

>>>>

\chapter{Improving performance using transfer learning}
\label{ch:transfer_learning}
%What we do: improve cancer detection/classification on medical imaging
%How we do it: transfer learning
This chapter proposes a technique to improve cancer detection and classification despite the lack of publicly available medical data. To achieve this, transfer learning is used.\\
First, a general definition of transfer learning is given. Its utility in this specific application is discussed as it is useful but not in any case. Second, the different steps involved in the process are described in order to get an overview of the whole transfer learning pipeline that was applied. Then, a section focuses on the processing of new datasets that are used in the final experiment. Finally, the latter and its results are discussed.
